### 2019-11-30 reports/media/loosely_acc.tex
start drawings

\documentclass{standalone}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning, calc, shapes, fit}

\begin{document}

\begin{tikzpicture}
  \tikzstyle{PE}=[rounded corners, draw, thick, minimum size=40pt, align=center]
  \tikzstyle{core}=[PE, draw=NavyBlue, fill=NavyBlue!20]
  \tikzstyle{hwacc}=[PE, draw=OliveGreen, fill=OliveGreen!20]
  \tikzstyle{bus}=[double arrow, draw=Orange, fill=Orange!20, thick,
  minimum width=20pt, double arrow head extend=2pt]

  \node (core2) at (0.4,0.4) [core] {};
  \node (core1) at (0.2,0.2) [core] {};
  \node (core0) at (0,0) [core] {CPU};

  \node (hwacc1) at (3,0.2) [hwacc] {ACC};
  \node (hwacc2) at (5,0.2) [hwacc] {ACC};

  \node (mainbus) at (-1, -2) [bus, anchor=west, minimum height=200pt] {};

  \node (dram) [draw, rounded corners, below= of mainbus, minimum width=60pt,
  minimum height=20pt, yshift=10pt, thick] {DRAM};

  \node at (dram.north) [bus, rotate=-90, anchor=east, scale=0.5, minimum height=35pt] {};

  \node at (core0.south) [bus, rotate=90, anchor=east, scale=0.5, minimum height=57pt] {};
  \node at (hwacc1.south) [bus, rotate=90, anchor=east, scale=0.5, minimum height=68pt] {};
  \node at (hwacc2.south) [bus, rotate=90, anchor=east, scale=0.5, minimum height=68pt] {};

  \node (gpc) [fit=(core0)(core1)(core2), rounded corners,
  dashed, draw, minimum height=60pt, label={[align=center]90:{General\\ purpose}}] {};
  \node (dsc) [fit=(hwacc1)(hwacc2), rounded corners, dashed,
  draw, minimum height=60pt, label={[align=center]90:{Domain\\ specific}}] {};

\end{tikzpicture}

\end{document}

### 2019-12-03 reports/media/loosely_acc.tex
add interrupts
add soc bounding box

@@
 
+  \begin{scope}[name=soc, local bounding box=socbb]
   \node (core2) at (0.4,0.4) [core] {};
@@
   \node (mainbus) at (-1, -2) [bus, anchor=west, minimum height=200pt] {};
-
-  \node (dram) [draw, rounded corners, below= of mainbus, minimum width=60pt,
-  minimum height=20pt, yshift=10pt, thick] {DRAM};
-
-  \node at (dram.north) [bus, rotate=-90, anchor=east, scale=0.5, minimum height=35pt] {};
 
@@
 
+  \draw[-latex] (hwacc1.west) -- ++(-1,0) node [anchor=south west] {\tiny int};
+  \draw[-latex] (hwacc2.west) -- ++(-0.25, 0) -- ++(0, 0.9) -- ++(-2.75, 0) node [anchor=south west] {\tiny int};
+  \end{scope}
+
+  \node (dram) [draw, rounded corners, below= of mainbus, minimum width=60pt,
+  minimum height=20pt, yshift=10pt, thick] {DRAM};
+
+  \node at (dram.north) [bus, rotate=-90, anchor=east, scale=0.5, minimum height=35pt] {};
+
+  \node [fit=(socbb), draw, dashed, rounded corners, thick, inner sep=6pt, label={320:SoC}] {};
+
 \end{tikzpicture}

### 2019-12-03 reports/media/loosely_acc.tex
add accelerator internals

@@
   minimum width=20pt, double arrow head extend=2pt]
+  \tikzstyle{accint}=[draw=OliveGreen, fill=OliveGreen!10, outer sep=1pt, inner sep=1pt,
+  node distance=0.5pt, opacity=0.85]
 
@@
   \node (hwacc1) at (3,0.2) [hwacc] {ACC};
+  \begin{scope}[name=completeacc, local bounding box=accbb, shift={(3, 0.2)}]
+    \node (reg0) [accint, minimum width=25pt, xshift=-5pt, minimum height=5pt, font=\tiny] {REG 0};
+    \node (reg1) [accint, minimum width=25pt, minimum height=5pt, below=of reg0, font=\tiny] {REG 1};
+    \node (reg2) [accint, minimum width=25pt, minimum height=5pt, below=of reg1, font=\tiny] {REG N};
+    \node (spm) [accint, minimum height=15pt, minimum width=5pt, align=center,
+    right=of reg0.north east, font=\tiny, anchor=north west] {S\\P\\M};
+    \node (accpe) [accint, minimum width=10pt, minimum height=10pt, above=of reg0.north west,
+    anchor=south west, font=\tiny] {PE};
+    \node (accctl) [accint, minimum width=10pt, minimum height=10pt, above=of spm.north east,
+    anchor=south east, font=\tiny] {CTL};
+  \end{scope}
+
   \node (hwacc2) at (5,0.2) [hwacc] {ACC};

### 2019-12-03 reports/media/tightly_acc.tex
add tightly coupled figure

\documentclass{standalone}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning, calc, shapes, fit, backgrounds}

\begin{document}
\begin{tikzpicture}
  \tikzstyle{coord}=[inner sep=0pt, outer sep=0pt, node distance=0pt]
  \tikzstyle{hwacc}=[rounded corners, draw=OliveGreen, fill=OliveGreen!20, thick, minimum size=40pt]
  \tikzstyle{control}=[draw=Purple, dashed, thick]
  \begin{scope}[name=datapath, local bounding box=dpathbb]

    % register file drawing
    \begin{scope}[name=rf, local bounding box=rfbb, shift={(0, -0.5)}]
      \node at (1,0) [anchor=south] {RF};
      \draw[fill=white, thick] (0,0) rectangle (2, -4);
      \foreach \i in {1,...,8} {
        \node (rfout\i) at (2, -0.5*\i+0.25) [coord] {};
        \node (rfin\i) at (0, -0.5*\i+0.25) [coord] {};
        \draw[thick] (0, -0.5*\i) -- (2, -0.5*\i);
      }
    \end{scope}

    % functional units
    \begin{scope}[name=fu, local bounding box=fubb, shift={(4, 0)}]
      \node at (0.75, 0) [anchor=south] {FUs};
      \begin{scope}[shift={(0.25, 0.15)}]
      \draw [fill=white, thick] (0, 0) -- (0, -1.75) -- (0.75, -2.5) -- (0, -3.25) -- (0, -5) -- (1.5, -3.5) -- (1.5, -1.5) -- cycle;
      \end{scope}
      \begin{scope}
        \draw [fill=white, thick] (0, 0) -- node [coord] (alua) {} (0, -1.75) -- (0.75, -2.5) -- (0, -3.25) -- node [coord] (alub) {}
        (0, -5) -- (1.5, -3.5) -- node [coord] (alux) {} (1.5, -1.5) -- cycle;
      \end{scope}
    \end{scope}

    % connections
    \draw (rfout1)  -| (alua);
    \draw (rfout2) -| ($(alub)!0.5!(rfout8)$) node (rfconn1) [coord, circle, fill=black, minimum size=4pt] {} -| (alub);
    \draw (alux) -- ++(1, 0) node (dataconn) [coord, circle, fill=black, minimum size=4pt] {} -- ++(0, 3.5) -- ++(-7, 0) |- (rfin1);

    % controller
    \node (ctl) at (0, -6.75) [draw, rectangle, rounded corners, minimum size=40pt, thick, fill=white] {Control};

    % tightly coupled acc
    \node (hwacc2) at (5.25, -6.5) [hwacc] {};
    \node (hwacc1) at (5, -6.75) [hwacc] {ACC};

    % accelerator connections
    \draw (hwacc2.east) -- ++(0.75, 0) -- ++(0, 7.75) -- ++(-7.5, 0) |- (rfin2);
    \draw (rfconn1) |- (hwacc1.200);
    \node (rfconn2) at (rfout1) [coord, circle, fill=black, minimum size=4pt, xshift=40] {};
    \draw (rfconn2) |- (hwacc1.160);
  \end{scope}

  \node (datamem) at (8.5, -2.5) [rounded corners, draw, thick, minimum size=50pt, align=center] {Data\\ Mem};
  \node (instmem) at (8.5, -6) [rounded corners, draw, thick, minimum size=50pt, align=center] {Instr\\ Mem};
  \draw (dataconn) -| (datamem.west);
  \draw (instmem.south) -- ++(0, -1.5) -| (ctl.south);

  % control lines
  \draw[control] (ctl.80) -- ++(0, 0.75) -- ++(5, 0) -- ++(0, 1.25);
  \draw[control] (ctl.90) -- ++(0, 1) -- ++(1, 0) -- ++(0, 0.55);
  \draw[control] (ctl.70) -- ++(0, 0.5) -- ++(1, 0);
  \draw[control] (ctl.70) -- ++(0, 0.5) -- ++(5, 0) -- (hwacc2.north);

  \begin{scope}[on background layer]
    \node [fit=(dpathbb), draw=NavyBlue, fill=NavyBlue!5, rounded corners, dashed, thick, inner sep=10pt,
    label={90:Simplified CPU Datapath}] {};
  \end{scope}
\end{tikzpicture}
\end{document}

### 2019-12-04 reports/media/hybrid_acc.tex
hybrid accelerator

\documentclass{standalone}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning, calc, shapes, fit, backgrounds, patterns}

\begin{document}
\begin{tikzpicture}
  \tikzstyle{accelement}=[rounded corners, draw, thick, minimum size=50pt, fill=white]
  \tikzstyle{port}=[semicircle, draw=Orange, fill=Goldenrod!10, anchor=south, thick]
  \tikzstyle{bibus}=[double arrow, draw=Orange, fill=Orange!20, thick,
  minimum width=20pt, double arrow head extend=2pt]
  \tikzstyle{ibus}=[single arrow, draw=Orange, fill=Orange!20, thick,
  minimum width=20pt, single arrow head extend=2pt]
  \tikzstyle{obus}=[single arrow, draw=Orange, fill=Orange!20, thick,
  minimum width=20pt, single arrow head extend=2pt, rotate=180]
  \tikzstyle{hwacc}=[rounded corners, draw=OliveGreen, fill=OliveGreen!10, thick]

  \begin{scope}[name=accstruct]
    \begin{scope}[name=acc, local bounding box=accbb]
      \node (accpe) [accelement] {PE};
      \node (accctl) at (0, -3) [accelement] {CTL};
    \end{scope}

    \begin{scope}[on background layer]
      \node (acc) [hwacc, fit=(accbb),
      minimum width=140pt, inner sep=10pt, label={270:Hybrid Accelerator}] {};
    \end{scope}

    \node (dmaport) at (acc.east) [port, minimum height=20pt, align=center,
    rotate=90] {DMA};
    \node (pathin) at (acc.west |- accpe.west) [port, rotate=270, anchor=south,
    minimum height=15pt] {};
    \node (pathout) at (acc.west |- accctl.west) [port, rotate=270, anchor=south,
    minimum height=15pt] {};

    \node (memconn) [bibus, anchor=west, minimum height=40pt, label={[align=center]0:{Main\\memory}}] at (dmaport.south) {};
    \node (fromdp) [ibus, anchor=east, minimum height=40pt, label={[align=center]180:{From CPU\\datapath}}] at (pathin.south) {};
    \node (todp) [obus, anchor=west, minimum height=40pt, label={[align=center]0:{To CPU\\datapath}}] at (pathout.south) {};
  \end{scope}

  \begin{scope}[name=op1, shift={(0, -7)}, local bounding box=mode1bb]
    \node (acc1) [hwacc, minimum size=40pt] {ACC};
    \node (inst) [draw, thick, rounded corners, left=of acc1, minimum size=40pt] {\tiny Instruction};
    \draw[-latex, very thick] (inst) -- node [anchor=south west, rotate=45, font=\footnotesize, align=center] {(control)\\addr,len} (acc1);
    \node (mconn1) at (acc1.east) [bibus, scale=0.5, anchor=west, minimum height=50pt] {};
    \node (dram1) at (mconn1.east) [draw, thick, minimum width=30pt, minimum height=60pt, anchor=west, label={270:Memory}] {};
    \draw [pattern=north west lines] (dram1.155) rectangle (dram1.335);
    \node at (dram1.east) [anchor=west, align=center, font=\footnotesize] {Plaintext or\\ciphertext};
  \end{scope}

  \node [draw,dashed, thick, fit=(mode1bb), inner sep=10pt, minimum width=250pt, label={270:Mode I: batch (de/en)crypt}, xshift=-12pt] {};

  \begin{scope}[name=op2, shift={(0, -12)}, local bounding box=mode2bb]
    \node (acc2) [hwacc, minimum size=40pt] {ACC};
    \node (dp) [draw=NavyBlue, thick, dashed, rounded corners, left=of acc2, minimum size=40pt, label={270:CPU Datapath}] {};
    \draw[-latex, very thick] (dp.20) -- node [anchor=south west, rotate=45, align=center, font=\footnotesize] {(data)\\plaintext} (dp.20 -| acc2.west);
    \draw[-latex, very thick] (dp.340 -| acc2.west) -- (dp.340);
    \node (mconn2) at (acc2.east) [bibus, scale=0.5, anchor=west, minimum height=50pt] {};
    \node (dram2) at (mconn2.east) [draw, thick, minimum width=30pt, minimum height=60pt, anchor=west, label={270:Memory}] {};
    \draw [pattern=north west lines] (dram2.155) rectangle (dram2.335);
    \node at (dram2.east) [anchor=west, align=center, font=\footnotesize] {Always\\ciphertext};
    \node at ([shift={(4pt, 30pt)}]mconn2) [align=center, rotate=45, font=\footnotesize] {ciphertext};
  \end{scope}

  \node [draw,dashed, thick, fit=(mode2bb), inner sep=10pt, minimum width=250pt,  label={270:Mode II: cryptographic operation}] {};

\end{tikzpicture}
\end{document}

### 2019-12-06 reports/media/loosely_acc.tex
remove second accelerator

@@
   \end{scope}
-
-  \node (hwacc2) at (5,0.2) [hwacc] {ACC};
-
-  \node (mainbus) at (-1, -2) [bus, anchor=west, minimum height=200pt] {};
+  \node (mainbus) at (-1, -2) [bus, anchor=west, minimum height=140pt] {};
 
@@
   \node at (hwacc1.south) [bus, rotate=90, anchor=east, scale=0.5, minimum height=68pt] {};
-  \node at (hwacc2.south) [bus, rotate=90, anchor=east, scale=0.5, minimum height=68pt] {};
 
@@
   dashed, draw, minimum height=60pt, label={[align=center]90:{General\\ purpose}}] {};
-  \node (dsc) [fit=(hwacc1)(hwacc2), rounded corners, dashed,
+  \node (dsc) [fit=(hwacc1), rounded corners, dashed, inner sep=10pt,
   draw, minimum height=60pt, label={[align=center]90:{Domain\\ specific}}] {};
@@
   \draw[-latex] (hwacc1.west) -- ++(-1,0) node [anchor=south west] {\tiny int};
-  \draw[-latex] (hwacc2.west) -- ++(-0.25, 0) -- ++(0, 0.9) -- ++(-2.75, 0) node [anchor=south west] {\tiny int};
   \end{scope}
@@
 
-  \node [fit=(socbb), draw, dashed, rounded corners, thick, inner sep=6pt, label={320:SoC}] {};
+  \node [fit=(socbb), draw, dashed, rounded corners, thick, inner sep=6pt, label={300:SoC}] {};
 

### 2019-12-06 reports/media/loosely_acc.tex
rename registers

@@
   \begin{scope}[name=completeacc, local bounding box=accbb, shift={(3, 0.2)}]
-    \node (reg0) [accint, minimum width=25pt, xshift=-5pt, minimum height=5pt, font=\tiny] {REG 0};
-    \node (reg1) [accint, minimum width=25pt, minimum height=5pt, below=of reg0, font=\tiny] {REG 1};
-    \node (reg2) [accint, minimum width=25pt, minimum height=5pt, below=of reg1, font=\tiny] {REG N};
+    \node (reg0) [accint, minimum width=25pt, xshift=-5pt, minimum height=5pt, font=\tiny] {MMR 0};
+    \node (reg1) [accint, minimum width=25pt, minimum height=5pt, below=of reg0, font=\tiny] {MMR 1};
+    \node (reg2) [accint, minimum width=25pt, minimum height=5pt, below=of reg1, font=\tiny] {MMR N};
     \node (spm) [accint, minimum height=15pt, minimum width=5pt, align=center,

### 2019-12-06 reports/media/tightly_acc.tex
rename
redraw

@@
 
+    % busses
+    \draw[ultra thick] (0, 1) -- (9, 1);
+    \draw[ultra thick] (0, -5.5) -- (9, -5.5);
+    \draw[ultra thick] (1, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (1, -0.5);
+    \draw[ultra thick] (5, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (5, -0.75);
+    \draw[ultra thick] (8.25, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (8.25, -1.75);
+
+    \draw[ultra thick] (1, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2);
+    \draw[ultra thick] (5, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2);
+    \draw[ultra thick] (8.25, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2.5);
+
     % register file drawing
     \begin{scope}[name=rf, local bounding box=rfbb, shift={(0, -0.5)}]
-      \node at (1,0) [anchor=south] {RF};
+      \node at (0.25,0) [anchor=south] {RF};
       \draw[fill=white, thick] (0,0) rectangle (2, -4);
@@
     \begin{scope}[name=fu, local bounding box=fubb, shift={(4, 0)}]
-      \node at (0.75, 0) [anchor=south] {FUs};
+      \node at (0.25, 0.25) [anchor=south] {FUs};
       \begin{scope}[shift={(0.25, 0.15)}]
@@
 
-    % connections
-    \draw (rfout1)  -| (alua);
-    \draw (rfout2) -| ($(alub)!0.5!(rfout8)$) node (rfconn1) [coord, circle, fill=black, minimum size=4pt] {} -| (alub);
-    \draw (alux) -- ++(1, 0) node (dataconn) [coord, circle, fill=black, minimum size=4pt] {} -- ++(0, 3.5) -- ++(-7, 0) |- (rfin1);
-
-    % controller
-    \node (ctl) at (0, -6.75) [draw, rectangle, rounded corners, minimum size=40pt, thick, fill=white] {Control};
-
-    % tightly coupled acc
-    \node (hwacc2) at (5.25, -6.5) [hwacc] {};
-    \node (hwacc1) at (5, -6.75) [hwacc] {ACC};
-
-    % accelerator connections
-    \draw (hwacc2.east) -- ++(0.75, 0) -- ++(0, 7.75) -- ++(-7.5, 0) |- (rfin2);
-    \draw (rfconn1) |- (hwacc1.200);
-    \node (rfconn2) at (rfout1) [coord, circle, fill=black, minimum size=4pt, xshift=40] {};
-    \draw (rfconn2) |- (hwacc1.160);
+    % tightly coupled accs
+    \begin{scope}[shift={(8, -2.5)}]
+      \node (hwacc2) at (0.25, 0.25) [hwacc] {};
+      \node (hwacc1) at (0, 0) [hwacc, align=center] {Tightly\\coupled\\ ACCs};
     \end{scope}
 
-  \node (datamem) at (8.5, -2.5) [rounded corners, draw, thick, minimum size=50pt, align=center] {Data\\ Mem};
-  \node (instmem) at (8.5, -6) [rounded corners, draw, thick, minimum size=50pt, align=center] {Instr\\ Mem};
-  \draw (dataconn) -| (datamem.west);
-  \draw (instmem.south) -- ++(0, -1.5) -| (ctl.south);
+  \end{scope}
 
-  % control lines
-  \draw[control] (ctl.80) -- ++(0, 0.75) -- ++(5, 0) -- ++(0, 1.25);
-  \draw[control] (ctl.90) -- ++(0, 1) -- ++(1, 0) -- ++(0, 0.55);
-  \draw[control] (ctl.70) -- ++(0, 0.5) -- ++(1, 0);
-  \draw[control] (ctl.70) -- ++(0, 0.5) -- ++(5, 0) -- (hwacc2.north);
+  % \node (datamem) at (8.5, -2.5) [rounded corners, draw, thick, minimum size=50pt, align=center] {Data\\ Mem};
+  % \node (instmem) at (8.5, -6) [rounded corners, draw, thick, minimum size=50pt, align=center] {Instr\\ Mem};
 
@@
     \node [fit=(dpathbb), draw=NavyBlue, fill=NavyBlue!5, rounded corners, dashed, thick, inner sep=10pt,
-    label={90:Simplified CPU Datapath}] {};
+    label={270:Simplified CPU Datapath}] {};
   \end{scope}

### 2019-12-06 reports/media/tightly_acc.tex
rotate FUs

@@
     \draw[ultra thick] (1, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (1, -0.5);
-    \draw[ultra thick] (5, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (5, -0.75);
+    \draw[ultra thick] (3.75, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, -3.5);
+    \draw[ultra thick] (6, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, -3.5);
     \draw[ultra thick] (8.25, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (8.25, -1.75);
@@
     \draw[ultra thick] (1, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2);
-    \draw[ultra thick] (5, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2);
+    \draw[ultra thick] (4.65, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2.5);
     \draw[ultra thick] (8.25, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2.5);
@@
     % functional units
-    \begin{scope}[name=fu, local bounding box=fubb, shift={(4, 0)}]
-      \node at (0.25, 0.25) [anchor=south] {FUs};
-      \begin{scope}[shift={(0.25, 0.15)}]
-      \draw [fill=white, thick] (0, 0) -- (0, -1.75) -- (0.75, -2.5) -- (0, -3.25) -- (0, -5) -- (1.5, -3.5) -- (1.5, -1.5) -- cycle;
+    \begin{scope}[name=fu, local bounding box=fubb, shift={(6.5, -2)}]
+      \node at (-1.5, 0.25) [anchor=south] {FUs};
+      \begin{scope}[shift={(0.25, 0.15)}, rotate=-90, scale=0.75]
+        \draw [fill=white, thick] (0, 0) -- (0, -1.75) -- (0.75, -2.5) -- (0, -3.25) -- (0, -5) -- (1.5, -3.5) -- (1.5, -1.5)
+        -- cycle;
       \end{scope}
-      \begin{scope}
-        \draw [fill=white, thick] (0, 0) -- node [coord] (alua) {} (0, -1.75) -- (0.75, -2.5) -- (0, -3.25) -- node [coord] (alub) {}
+      \begin{scope}[rotate=-90, scale=0.75]
+        \draw [fill=white, thick] (0, 0) -- node [coord] (alua) {} (0, -1.75) -- (0.75, -2.5) -- (0, -3.25)
+        -- node [coord] (alub) {}
         (0, -5) -- (1.5, -3.5) -- node [coord] (alux) {} (1.5, -1.5) -- cycle;

### 2019-12-06 reports/media/hybrid_acc.tex
redraw hybrid

@@
 
+  \begin{scope}[shift={(1, 0)}]
     \begin{scope}[name=accstruct]
       \begin{scope}[name=acc, local bounding box=accbb]
-      \node (accpe) [accelement] {PE};
-      \node (accctl) at (0, -3) [accelement] {CTL};
+        \node (accpe) [accelement] {Datapath};
       \end{scope}
+
+      \node (accctl) at (-2.25, 0) [accelement, fill opacity=0.8, text opacity=1] {Control};
 
@@
         \node (acc) [hwacc, fit=(accbb),
-      minimum width=140pt, inner sep=10pt, label={270:Hybrid Accelerator}] {};
+        minimum width=120pt, inner sep=10pt, label={270:Hybrid Accelerator}] {};
+        \node (cpudp) at (-2.25,0)  [draw=NavyBlue, fill=NavyBlue!10, thick, dashed, rounded corners,
+        anchor=east, minimum height=70pt, minimum width=70pt, label={[align=center]270:{CPU\\Datapath}}] {};
       \end{scope}
@@
       rotate=90] {DMA};
-    \node (pathin) at (acc.west |- accpe.west) [port, rotate=270, anchor=south,
-    minimum height=15pt] {};
-    \node (pathout) at (acc.west |- accctl.west) [port, rotate=270, anchor=south,
-    minimum height=15pt] {};
 
-    \node (memconn) [bibus, anchor=west, minimum height=40pt, label={[align=center]0:{Main\\memory}}] at (dmaport.south) {};
-    \node (fromdp) [ibus, anchor=east, minimum height=40pt, label={[align=center]180:{From CPU\\datapath}}] at (pathin.south) {};
-    \node (todp) [obus, anchor=west, minimum height=40pt, label={[align=center]0:{To CPU\\datapath}}] at (pathout.south) {};
+      \node (memconn) [bibus, anchor=west, minimum height=30pt, label={[align=center,font=\footnotesize]0:{Main\\memory}}] at (dmaport.south) {};
+    \end{scope}
   \end{scope}
 
-  \begin{scope}[name=op1, shift={(0, -7)}, local bounding box=mode1bb]
+  \begin{scope}[name=op1, shift={(0.5, -4.5)}, local bounding box=mode1bb]
     \node (acc1) [hwacc, minimum size=40pt] {ACC};
@@
 
-  \begin{scope}[name=op2, shift={(0, -12)}, local bounding box=mode2bb]
+  \begin{scope}[name=op2, shift={(0.5, -9.5)}, local bounding box=mode2bb]
     \node (acc2) [hwacc, minimum size=40pt] {ACC};

### 2019-12-06 reports/media/tightly_acc.tex
squeeze picture

@@
     % busses
-    \draw[ultra thick] (0, 1) -- (9, 1);
-    \draw[ultra thick] (0, -5.5) -- (9, -5.5);
-    \draw[ultra thick] (1, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (1, -0.5);
-    \draw[ultra thick] (3.75, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, -3.5);
-    \draw[ultra thick] (6, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, -3.5);
-    \draw[ultra thick] (8.25, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (8.25, -1.75);
+    \draw[ultra thick] (0, 0.25) -- ++(9, 0);
+    \draw[ultra thick] (0, -5) -- ++(9, 0);
+    \draw[ultra thick] (1, 0.25) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, -1);
+    \draw[ultra thick] (3.75, 0.25) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, -2.5);
+    \draw[ultra thick] (6, 0.25) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, -2.5);
+    \draw[ultra thick] (8.25, 0.25) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (8.25, -1.75);
 
-    \draw[ultra thick] (1, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2);
-    \draw[ultra thick] (4.65, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2.5);
-    \draw[ultra thick] (8.25, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2.5);
+    \draw[ultra thick] (1, -5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2);
+    \draw[ultra thick] (4.65, -5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2.5);
+    \draw[ultra thick] (8.25, -5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2.5);
 

### 2019-12-06 reports/media/loosely_acc.tex
datapath
full word interrupt

@@
     \node (accpe) [accint, minimum width=10pt, minimum height=10pt, above=of reg0.north west,
-    anchor=south west, font=\tiny] {PE};
+    anchor=south west, font=\tiny] {DP};
     \node (accctl) [accint, minimum width=10pt, minimum height=10pt, above=of spm.north east,
@@
 
-  \draw[-latex] (hwacc1.west) -- ++(-1,0) node [anchor=south west] {\tiny int};
+  \draw[-latex] (hwacc1.west) -- ++(-1,0) node [anchor=south west, xshift=-4pt] {\tiny interrupt};
   \end{scope}

### 2019-12-06 reports/paper.tex
start writing

\documentclass[10pt,conference]{IEEEtran}
\usepackage[dvipsnames]{xcolor}
\usepackage{standalone}
\usepackage{tikz}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{booktabs}
\usepackage{tabu}
\usepackage[letterpaper]{geometry}
\usepackage[colorlinks]{hyperref}
\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2cm,rmargin=2cm,columnsep=0.8cm}
\usetikzlibrary{positioning, calc, shapes, fit, backgrounds, patterns}

\title{\textbf{Hardware accelerator topologies in heterogeneous systems: an evaluation in the
    security domain}}
\author{Bruno Morais}
\date{}

\begin{document}

\maketitle

\begin{abstract}
  Hardware accelerators (HWACCs) have driven performance gains for
  domain specific applications which leverage highly optimized computation
  cores. However, the traditional accelerator access topology as an add-on to
  general purpose processors through shared memory space/bus, reveals performance
  issues as the number of HWACCs grow and systems become
  communication-bound.
  On the other hand, efficient development and research of HWACCs
  that are closer to a general purpose processor's datapath is seen as a
  prohibitive task due to the required microarchitecture knowledge and lack of
  tools to explore the design space. This has in turn hindered the exploration of
  such architectures for gains in either performance or security spectrums.
  RISC-V projects made available in the last few years provide a framework that
  greatly eases microarchitecture research, enabling further experimentation
  into security and performance aspects for heterogeneous platforms.
  This work uses a customized RISC-V SoC to explore performance trade-offs
  between different HWACC topologies (in-datapath, memory-mapped) for embedded
  systems in the security domain by implementing an IP core for cryptographic
  primitive acceleration.
  % results also go in here

\end{abstract}

\section{Introduction}

\section{Related work}

\subsection{Hardware accelerators?}
% Tightly vs loosely coupled hwaccs

\subsection{RISC-V instruction set extensions}
% Xcrypto

\section{Background}

\subsection{Heterogeneous systems and HWACCs}

\begin{figure}
  \centering
  \include{media/loosely_acc}
  \caption{Loosely-coupled HWACCs: typical memory mapped HWACC usage in a heterogenous architecture.}
\end{figure}

\begin{figure}
  \centering
  \scalebox{0.75}{
  \begin{minipage}{0.5\textwidth}
    \centering
    \include{media/tightly_acc}
  \end{minipage}
  }
  \caption{Tightly-coupled HWACCs: accelerator is moved into CPU datapath,
    similar to Functional Units (FUs).}
\end{figure}

\begin{figure}
  \centering
  \include{media/hybrid_acc}
  \caption{Hybrid cryptographic HWACCs: \textbf{upper}: HWACC is directly accessible through CPU datapath and
    integrated with memory hierarchy; \textbf{lower}: two operation modes; I: batch
  background processing of memory region (CPU not taxed); II: cryptographic
  operation where plaintext is only visible inside CPU datapath.}
\end{figure}

\subsection{Embedded security: lightweight ciphers}

The industry standard ciphers might impose too much of a burden on deeply
embedded, low power systems that need the ability to communicate securely over
an unsecured channel. Thus, different organizations have hosted competitions to
foster the development of lightweight ciphers, targeting both resource-limited
software and hardware implementations.

In this evaluation, it is assumed that the object of study is such a system,
with strict area and power limitations. The Simon~\cite{Beaulieu2015} cipher family is chosen as a
lightweight cipher; it is a hardware-optimized cipher family developed by the
NSA. Although faced with controversies due to polarized views towards the
authors, it is an ISO standardized cipher.

\subsection{RISC-V ecosystem}

\section{Experimental setup}

\section{Evaluation}

\section{Future work}

As future work, there is much room for improvement; better understanding of how
to leverage the memory coherence hierarchy in the hybrid accelerator model
should lead to better performance.

Also, a set of different, reutilizable cryptographic primitives can be further
explored and integrated into a larger multi-accelerator framework for
acceleration of other demanded cryptographic functions such as hash functions
and possible compositions of primitives for message authentication, for instance.

These require a more thorough and complex modification of the available
toolchain and datapath microarchitecture, as it is likely that the standard RoCC
interface will not be able to provide the desired flexibility and control
granularity levels for detailed exploration.

\section{Conclusions}

\bibliography{paper}
\bibliographystyle{ieeetr}

\end{document}

### 2019-12-06 reports/paper.tex
write some

@@
 
+\begin{figure}
+  \centering
+  \include{media/loosely_acc}
+  \caption{Loosely-coupled HWACCs: typical memory mapped HWACC usage in a heterogenous architecture.}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \resizebox{0.3\textwidth}{!}{
+    \begin{minipage}{0.5\textwidth}
+      \centering
+      \include{media/tightly_acc}
+    \end{minipage}
+  }
+  \caption{Tightly-coupled HWACCs: accelerator is moved into CPU datapath,
+    similar to Functional Units (FUs).}
+\end{figure}
+
 \section{Related work}
@@
 \section{Background}
-
-\subsection{Heterogeneous systems and HWACCs}
-
-\begin{figure}
-  \centering
-  \include{media/loosely_acc}
-  \caption{Loosely-coupled HWACCs: typical memory mapped HWACC usage in a heterogenous architecture.}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \scalebox{0.75}{
-  \begin{minipage}{0.5\textwidth}
-    \centering
-    \include{media/tightly_acc}
-  \end{minipage}
-  }
-  \caption{Tightly-coupled HWACCs: accelerator is moved into CPU datapath,
-    similar to Functional Units (FUs).}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \include{media/hybrid_acc}
-  \caption{Hybrid cryptographic HWACCs: \textbf{upper}: HWACC is directly accessible through CPU datapath and
-    integrated with memory hierarchy; \textbf{lower}: two operation modes; I: batch
-  background processing of memory region (CPU not taxed); II: cryptographic
-  operation where plaintext is only visible inside CPU datapath.}
-\end{figure}
 
@@
 
+The RISC-V ecosystem is rapidly growing, with many different implementations of
+the RISC-V ISA standard currently available online. The complete GNU toolchain
+is also available for the architecture and its standard extensions.
+
+There are several alternatives in order to assemble a complete System on Chip
+(SoC) for experimentation or synthesis purposes. Several different vendors /
+open source community-provided designs can be used to kickstart development.
+
+To assemble an entire SoC for cycle-accurate simulation, UC Berkeley's Chipyard~\cite{Chipyard}
+is chosen.
+
+\begin{figure}
+  \centering
+  \resizebox{0.45\textwidth}{!}{
+    \begin{minipage}{0.5\textwidth}
+      \centering
+      \include{media/hybrid_acc}
+    \end{minipage}
+  }
+  \caption{Hybrid crypto HWACCs: \textbf{upper}: HWACC is directly accessible through CPU datapath and
+    integrated with memory hierarchy; \textbf{lower}: two operation modes; I: batch
+    background processing of memory region (CPU not taxed); II: cryptographic
+    operation where plaintext is only visible inside CPU datapath.}
+  \label{fig:hybrid}
+\end{figure}
+
+\section{The Hybrid Crypto Accelerator}
+
+Going one step further than the two classic topologies used for accelerators
+discussed previously, we present a slightly different hybrid approach which has
+some interesting characteristics. Figure~\ref{fig:hybrid} shows the concept and
+possible operation modes of the hybrid crypto accelerator.
+
+The hybrid crypto accelerator is distinct from the tightly-coupled topology in
+the way that it has a DMA port for direct access to the coherent memory
+hierarchy. This allows the accelerator to directly request data to be loaded and
+stored, enabling two different modes of operation.
+
+\subsection{Operation mode I: batch processing}
+
+In this operation mode, specific instructions configure the accelerator to
+batch perform encryption or decryption over a memory region. The accelerator
+then proceeds to work while the CPU is left free for any other tasks that might
+be waiting for CPU time.
+
+\subsection{Operation mode II: cryptographic operation}
+
+Differently from mode I, this mode allows for operation in the security domain,
+isolating plaintext and ciphertext completely in the CPU datapath and memory.
+
+In this mode, data is moved to/from memory by the CPU, through the accelerator,
+which transparently encrypts or decrypts the data stored/loaded. Note that in
+this mode, actual data (words) in the CPU datapath is passed in/out of the
+accelerator, not control (load/store).
+
 \section{Experimental setup}
 
+In order to understand the area and performance trade-offs between the usage of
+different system topologies, both a reference software implementation and an IP
+core that performs the Simon cipher are implemented and tested on a RISC-V core.
+
+The first step is to verify basic functionality by means of functional simulations.
+
+\subsection{Functional simulation}
+
+Functional simulation is accomplished with Spike~\cite{spike}, which is a RISC-V
+instruction set simulator. Spike allows for execution of riscv64 binaries, and
+also allows for implementation of C++ extensions that emulate the
+functionalities of both memory-mapped peripherals and RoCC accelerators. Both
+extensions are implemented to emulate functionality of different Simon
+accelerators, and checked for result correctness against the reference software
+implementation.
+
+\subsection{Simon HWACCs}
+
+After the functional simulations are performed with correct results, the Simon
+cipher IP core was implemented in Chisel~\cite{chisel}. This was a necessary
+choice since the infrastructure used to build the SoC to be evaluated is
+completely built using Chisel.
+
+The core Simon cipher functionality is implemented as the core IP and is
+re-utilized to build three different accelerator types: memory-mapped
+(loosely-coupled), RoCC (tightly-coupled and hybrid). In essence the the
+accelerators are built by constructing wrappers around the common core.
+
+The first two accelerators have similar functionality: the user must initialize the
+accelerator by storing a key, at which point the acelerator core performs
+necessary key expansion and waits for input data that is to be
+encrypted/decrypted. Those accelerators support two different Simon widths:
+Simon64/128 and Simon128/128.
+
+The memory-mapped accelerator can operate in two different ways: i) unattended
+operation --- ECB mode only, in which all necessary rounds are performed over a word until
+completion of encryption/decryption process, or ii) interactive operation, where
+software issues one round at a time, which enables software implementation of
+CBC or other modes.
+
+The tightly-coupled accelerator only operates interactively; that is, the
+software manually issues an instruction that computes a round repetitively
+until the complete process is done; encryption modes are thus
+implemented in software.
+
+The hybrid accelerator also needs to be initialized with a key. However, due to
+development constraints, the accelerator only supports Simon64/128 in ECB mode.
+
+\subsection{Full-scale SoC simulation}
+
+Chipyard is used to generate synthesizable Verilog for the
+entire SoC, including RISC-V CPU core and accelerators under test. The tool also
+contains the necessary scripts to produce a cycle-accurate simulation of the
+SoC, compiled with Verilator. After configuration of the environment, the Simon
+chisel implementation is integrated in the SoC.
+
+In Chipyard the option of either building the SoC using in-order (Rocket) or
+out-of-order (BOOM) cores is given to the user. SoCs are built using both
+alternatives for evaluation.
+
+\subsection{Synthesis metrics}
+
+Unfortunately, while the output from Chipyard is indeed synthesizable Verilog,
+no support for targeting FPGA boards is readily available. Instead, the focus of
+the tool is to enable VLSI flows for taping out custom ASICs.
+
+However, Chipyard shares much of common RISC-V infrastructure that is maintained
+by the CHIPS Alliance, it is possible to modify other projects that also use the
+same infrastructure, and do target FPGA boards to include our accelerators. This
+flow is used mainly for area evaluation purposes and not fully concerned with
+actually running code on an FPGA prototyping target. SiFive's Freedom Platform
+dev kit is chosen for this task.
+
 \section{Evaluation}
+
+\subsection{Security implications}
+
+It is of note that while this work implements a cryptographic primitive that can
+be used in-hardware to enable acceleration of ciphers, it is a proof-of-concept
+level rudimentary implementation.
+
+Under more critical scrutiny there would be a few immediately reconizeable
+issues:
+
+\begin{itemize}
+  \item In some configurations, accelerators can only perform in ECB mode in
+    hardware, limiting both security and performance. To overcome this, the
+    accelerator implementation needs to be extended to be more flexible/complex
+    and include such operation modes.
+  \item Due to the use of generic instruction / RoCC interface, accelerators
+    can be exploited by attacker at unprivileged level. To overcome this,
+    accelerators and toolchain must be modified to use customized instructions,
+    which can be configured for certain privilege levels only
+\end{itemize}
 
@@
 to leverage the memory coherence hierarchy in the hybrid accelerator model
-should lead to better performance.
+should lead to better performance; accelerator can be developed further to
+accept more encryption modes, including parallelization; security can be
+hardened by enforcing privilege levels at the hardware level, to name a few.
 

### 2019-12-07 reports/media/simonround.tex
simon round drawing

\documentclass{standalone}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning, calc, shapes, fit, backgrounds, patterns}

\begin{document}
\begin{tikzpicture}
\tikzstyle{roundblock}=[draw=Purple, thick, fill=Purple!10, minimum width=30pt, minimum height=15pt]
\tikzstyle{function}=[draw=Orange, circle, thick, fill=Orange!10, minimum size=15pt,
font=\tiny\bfseries, node distance=5pt, inner sep=0pt]
\tikzstyle{XOR}=[draw,circle, minimum size=10pt, thick, append after command={
      [shorten >=\pgflinewidth, shorten <=\pgflinewidth,]
      (\tikzlastnode.north) edge[thick] (\tikzlastnode.south)
      (\tikzlastnode.east) edge[thick] (\tikzlastnode.west)},
    node distance=10pt]
\tikzstyle{junct}=[inner sep=0pt, circle, draw, fill=black, minimum size=2pt]

% inputs
\node (inpx) [roundblock] {$x_{i+1}$};
\node (inpy) [roundblock, right=of inpx, xshift=25pt] {$x_i$};

% shifts
\node (s1) [function, below=of inpx.south east, xshift=10pt] {S\textsuperscript{1}};
\node (s8) [function, below=of s1] {S\textsuperscript{8}};
\node (s2) [function, below=of s8] {S\textsuperscript{2}};

% and
\node (and) at ($(s1)!0.5!(s8)$) [function, draw=ForestGreen, fill=ForestGreen!10, xshift=30pt] {\&};

% xors
\node (xor1) at (and -| inpy) [XOR] {};
\node (xor2) at (s2 -| xor1) [XOR] {};
\node (xor3) [XOR, below=of xor2] {};

\node (key) [right=of xor3, xshift=-20pt] {$k_i$};

% connections
\draw[-latex] (s1) -- (and);
\draw[-latex] (s8) -- (and);
\draw[-latex] (and) -- (xor1);
\draw[-latex] (s2) -- (xor2);
\draw[-latex] (inpy) -- (xor1);
\draw[-latex] (xor1) -- (xor2);
\draw[-latex] (xor2) -- (xor3);
\draw[-latex] (inpx.south) |- node (junct1) [junct] {} (s1);
\draw[-latex] (junct1) |- node (junct2) [junct] {} (s8);
\draw[-latex] (junct2) |- node (junct3) [junct] {} (s2);
\draw[-latex] (key) -- (xor3);

% out
\node (outx) [roundblock,  below=of inpx, yshift=-80pt] {$x_{i+2}$};
\node (outy) [roundblock, right=of outx, xshift=25pt] {$x_{i+1}$};

\draw[-latex] (xor3.south) -- ++(0, -0.25) node (coord1) {} -- ([yshift=10pt]outx.north) -- (outx.north);
\draw[-latex] (junct3) -- (coord1 -| junct3) -- ([yshift=10pt]outy.north) -- (outy.north);

\end{tikzpicture}
\end{document}

### 2019-12-07 reports/paper.tex
write more

@@
 
+The Simon family of ciphers offers different possibilities for both block and
+key sizes. In all cases, both the round and key expansion functions make use
+only of bitwise \texttt{XOR}, \texttt{AND}, and left and right circular shifts.
+Figure~\ref{fig:simonround} shows the Feistel stepping of its round function.
+
+\begin{figure}
+  \centering
+  \include{media/simonround}
+  \caption{Simon's round function Feistel stepping. \textbf{S\textsuperscript{i}} are
+    circular left shifts by i bits; \textbf{\&} is a bitwise \texttt{AND}
+    operation and $\oplus$ are bitwise \texttt{XOR} operations.}
+  \label{fig:simonround}
+\end{figure}
+
+The number of necessary rounds is determined by the configuration of the cipher.
+In this work we explore only the Simon64/128 and Simon128/128 configurations,
+which require a number of 44 and 68 rounds per block, respectively.
+In the nomenclature Simon\textbf{N}/\textbf{M}, \textbf{N} is the block size and
+\textbf{M} is the key size in bits.
+
 \subsection{RISC-V ecosystem}
@@
 
-Going one step further than the two classic topologies used for accelerators
-discussed previously, we present a slightly different hybrid approach which has
+Going one step further than the two previously discussed topologies used for
+accelerators, we present a slightly different hybrid approach which has
 some interesting characteristics. Figure~\ref{fig:hybrid} shows the concept and

### 2019-12-07 evaluation/src/mmio_ecb.c
fix wrong initialization, auto-reload tests were invalid

@@ -40,7 +40,7 @@ TestResult test_mmio_ecb_auto(unsigned int testSize, uint8_t* testData) {
 
   // initialize acc
   simon_mmio_initialize((uint8_t *)key,
-                        SIMON_MMIO_SCONF_SINGLE | SIMON_MMIO_SCONF_ENCDEC, 1);
+                        SIMON_MMIO_SCONF_ENCDEC, 1);
 
   test_start(&result);
   for (i = 0; i <testSize; i += SIMON_64_128_BLOCK_SIZE) {

### 2019-12-07 riscv/src/simon/mmio.c

@@ -8,7 +8,7 @@ void simon_mmio_initialize(uint8_t* key, uint8_t config, uint8_t wait) {
 
   // initialize
   reg_write64(SIMON_MMIO_BASE + SIMON_MMIO_REG_SCONF,
-              SIMON_MMIO_SCONF_SINGLE | SIMON_MMIO_SCONF_ENCDEC);
+              config);
   reg_write64(SIMON_MMIO_BASE + SIMON_MMIO_REG_KEY1, kw1);
   reg_write64(SIMON_MMIO_BASE + SIMON_MMIO_REG_KEY2, kw2);
 

### 2019-12-07 reports/media/plots.py
generate plots with matplotlib

@@ -1,0 +1,84 @@
+"""Generate plots for results."""
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import numpy
+
+TEST_NAMES = ["SW/ECB", "SW/CBC", "MMIO/ECB (automatic)",
+              "MMIO/ECB (interactive)", "MMIO/CBC", "RoCC/ECB",
+              "RoCC/CBC", "Hybrid/EBC"]
+
+ROCKET_RESULTS = "../../evaluation/rocket.results"
+BOOM_RESULTS = "../../evaluation/boom.results"
+
+
+def parse_results(data):
+    """Parse results."""
+    return [(int(d[0]), int(d[1])) for d in [d.split(",") for d in data]]
+
+
+if __name__ == "__main__":
+    plt.style.use('bmh')
+
+    # load results
+    with open(ROCKET_RESULTS, "r") as rocketdata:
+        rocket = parse_results(rocketdata.readlines())
+
+    with open(BOOM_RESULTS, "r") as boomdata:
+        boom = parse_results(boomdata.readlines())
+
+    if len(boom) != len(rocket) or len(boom) < len(TEST_NAMES):
+        print("ERROR: incorrect result formatting")
+        exit(1)
+
+    # get slowest (more cycles) for normalization purposes
+    rocket_cycles = [data[0] for data in rocket]
+    rocket_insts = [data[1] for data in rocket]
+    boom_cycles = [data[0] for data in boom]
+    boom_insts = [data[1] for data in boom]
+    slowest_ebc, _ = rocket[0]
+    slowest_cbc, _ = rocket[1]
+
+    # horizontal bar plots
+    # plot 1 is ECB mode cycle count normalized to Rocket
+    fig, ax = plt.subplots()
+    ecb_benchmarks = ["2-way\nBOOM", "MMIO\n(auto)", "MMIO\n(single)",
+                      "RoCC", "Hybrid\n(batch)"]
+    ecb_cycles = [boom_cycles[0], rocket_cycles[2],
+                  rocket_cycles[3], rocket_cycles[5], rocket_cycles[7]]
+    ecb_speedup = [slowest_ebc/cycles for cycles in ecb_cycles]
+
+    ecb_data_sorted = sorted(zip(ecb_speedup, ecb_benchmarks))
+    ecb_sorted_names = [x for _, x in ecb_data_sorted]
[…]

### 2019-12-07 reports/paper.tex
update report

@@
   \include{media/simonround}
-  \caption{Simon's round function Feistel stepping. \textbf{S\textsuperscript{i}} are
-    circular left shifts by i bits; \textbf{\&} is a bitwise \texttt{AND}
+  \caption{Simon's round function Feistel stepping. \textbf{S\textsuperscript{j}} are
+    circular left shifts by j bits; \textbf{\&} is a bitwise \texttt{AND}
     operation and $\oplus$ are bitwise \texttt{XOR} operations.}
@@
 
-The memory-mapped accelerator can operate in two different ways: i) unattended
+The memory-mapped accelerator can operate in two different ways: i) automatic
 operation --- ECB mode only, in which all necessary rounds are performed over a word until
@@
 
-\section{Evaluation}
+\section{Evaluation results}
+
+\subsection{Performance}
+
+To evaluate performance, we consider the case where a plaintext block with a size of
+1 kB is encrypted using different implementations of the Simon cipher, yielding
+eight different benchmarks:
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{media/ecb_speedup}
+  \caption{Speedup using different accelerator configurations in ECB mode.}
+  \label{fig:ecbspeedup}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{media/cbc_speedup}
+  \caption{Speedup using different accelerator configurations in CBC mode.}
+  \label{fig:cbcspeedup}
+\end{figure}
+
+\subsection{Area}
 

### 2019-12-08 evaluation/src/evaluate8.c
fix test size

@@ -18,7 +18,7 @@ void do_test(void) {
   // block = *((uint64_t *)test_block);
   test_start(&result);
   // perform encryption rounds
-  TOOSLY_ENC(localData, TEST_DATA_SIZE);
+  TOOSLY_ENC(localData, TEST_DATA_SIZE/8);
 
   asm volatile("fence");
   test_end(&result);

### 2019-12-08 reports/media/plots.py
update plot script, blackify

@@ -1,12 +1,20 @@
 """Generate plots for results."""
 import matplotlib
+
 matplotlib.use("Agg")
 import matplotlib.pyplot as plt
 import numpy
 
-TEST_NAMES = ["SW/ECB", "SW/CBC", "MMIO/ECB (automatic)",
-              "MMIO/ECB (interactive)", "MMIO/CBC", "RoCC/ECB",
-              "RoCC/CBC", "Hybrid/EBC"]
+TEST_NAMES = [
+    "SW/ECB",
+    "SW/CBC",
+    "MMIO/ECB (automatic)",
+    "MMIO/ECB (interactive)",
+    "MMIO/CBC",
+    "RoCC/ECB",
+    "RoCC/CBC",
+    "Hybrid/EBC",
+]
 
 ROCKET_RESULTS = "../../evaluation/rocket.results"
 BOOM_RESULTS = "../../evaluation/boom.results"
@@ -18,7 +26,7 @@ def parse_results(data):
 
 
 if __name__ == "__main__":
-    plt.style.use('bmh')
+    plt.style.use("bmh")
 
     # load results
     with open(ROCKET_RESULTS, "r") as rocketdata:
@@ -42,43 +50,70 @@ if __name__ == "__main__":
     # horizontal bar plots
     # plot 1 is ECB mode cycle count normalized to Rocket
     fig, ax = plt.subplots()
-    ecb_benchmarks = ["2-way\nBOOM", "MMIO\n(auto)", "MMIO\n(single)",
-                      "RoCC", "Hybrid\n(batch)"]
-    ecb_cycles = [boom_cycles[0], rocket_cycles[2],
-                  rocket_cycles[3], rocket_cycles[5], rocket_cycles[7]]
-    ecb_speedup = [slowest_ebc/cycles for cycles in ecb_cycles]
+    ecb_benchmarks = [
+        "2-way\nBOOM",
+        "MMIO\n(auto)",
+        "MMIO\n(single)",
+        "RoCC",
+        "Hybrid\n(batch)",
+    ]
+    ecb_cycles = [
+        boom_cycles[0],
+        rocket_cycles[2],
+        rocket_cycles[3],
+        rocket_cycles[5],
+        rocket_cycles[7],
+    ]
+    ecb_speedup = [slowest_ebc / cycles for cycles in ecb_cycles]
 
     ecb_data_sorted = sorted(zip(ecb_speedup, ecb_benchmarks))
     ecb_sorted_names = [x for _, x in ecb_data_sorted]
[…]

### 2019-12-08 reports/paper.tex
update paper

@@
 operation --- ECB mode only, in which all necessary rounds are performed over a word until
-completion of encryption/decryption process, or ii) interactive operation, where
+completion of encryption/decryption process, or ii) interactive or single operation, where
 software issues one round at a time, which enables software implementation of
@@
 
-To evaluate performance, we consider the case where a plaintext block with a size of
-1 kB is encrypted using different implementations of the Simon cipher, yielding
-eight different benchmarks:
-
 \begin{figure}
@@
   \includegraphics[width=\linewidth]{media/ecb_speedup}
-  \caption{Speedup using different accelerator configurations in ECB mode.}
+  \caption{Speedup using different accelerator configurations in ECB mode.
+    Values are relative to the in-order pure software implementation.}
   \label{fig:ecbspeedup}
@@
   \label{fig:cbcspeedup}
+\end{figure}
+
+To evaluate performance, we consider the case where a plaintext block with a size of
+1 kB is encrypted using different implementations of the Simon cipher, yielding
+eight different benchmarks:
+
+\begin{itemize}
+\item Pure software: ECB and CBC mode
+\item MMIO accelerator, single: ECB and CBC mode
+\item MMIO accelerator, automatic: ECB mode
+\item Tightly-coupled accelerator: ECB and CBC mode
+\item Hybrid accelerator: ECB mode
+\end{itemize}
+
+Usage of the MMIO accelerator in automatic mode highlights the characteristics
+of a heterogeneous system that is computation-bound, whereas usage of it in the
+single mode intends to model a communication-bound architecture.
+
+The reference software implementation is used as a baseline,
+Figures~\ref{fig:ecbspeedup},\ref{fig:cbcspeedup} show the relative speedup
+(computed from the total cycle count for each of the benchmarks) of alternative
+implementations using accelerators or a 2-way BOOM core for encryption in ECB
+and CBC mode, respectively.
+
+% TODO small interpretation paragraph here
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{media/scatter_results}
+  \caption{Distribution of all benchmark results with respect to both total
+    number of instructions retired by processor and total number of cycles
+    required to complete operations.}
+  \label{fig:scatter}
 \end{figure}

### 2019-12-08 reports/media/plots.py

@@ -3,13 +3,14 @@ import matplotlib
 
 matplotlib.use("Agg")
 import matplotlib.pyplot as plt
+import matplotlib.ticker as ticker
 import numpy
 
 TEST_NAMES = [
     "SW/ECB",
     "SW/CBC",
-    "MMIO/ECB (automatic)",
-    "MMIO/ECB (interactive)",
+    "MMIO/ECB (auto)",
+    "MMIO/ECB (single)",
     "MMIO/CBC",
     "RoCC/ECB",
     "RoCC/CBC",
@@ -117,3 +118,18 @@ if __name__ == "__main__":
     ax.grid(axis="y", b=False)
 
     plt.savefig("cbc_speedup.pdf")
+
+    # scatter plot
+    fig, ax = plt.subplots()
+
+    for cycle, inst, name in zip(rocket_cycles, rocket_insts, TEST_NAMES):
+        ax.plot(cycle, inst, "o", label=name)
+    ax.xaxis.set_major_formatter(ticker.EngFormatter())
+    ax.yaxis.set_major_formatter(ticker.EngFormatter())
+    ax.legend()
+    ax.set_xlabel("Cycles")
+    ax.set_ylabel("Instructions retired")
+    ax.set_title(
+        "Instructions retired vs Cycles for benchmarks on\nin-order core"
+    )
+    plt.savefig("scatter_results.pdf")

### 2019-12-08 reports/paper.tex
wording
wording II

@@
   \caption{Tightly-coupled HWACCs: accelerator is moved into CPU datapath,
-    similar to Functional Units (FUs).}
+    operating similarly to microarchitectural Functional Units (FUs).}
 \end{figure}
@@
 
-The industry standard ciphers might impose too much of a burden on deeply
+Industry standard ciphers such as AES might impose too much of a burden on deeply
 embedded, low power systems that need the ability to communicate securely over

### 2019-12-08 reports/paper.tex
add a bit of interpretation

@@
 % TODO small interpretation paragraph here
+The hybrid accelerator is significantly faster than all other implementations
+tested. This is to be expected since the accelerator itself performs the memory
+requests without intervention of the CPU, directly into the memory bus. The
+memory-mapped accelerator in the automatic mode comes in as second fastest. This
+is also to be expected in comparison with the RoCC accelerator for example,
+since the latter is run in interactive mode, that is, the application code
+issues each round sequentially and sequential rounds are not immediately
+executed by the CPU, due to buffering and communication logic in the RoCC
+adapter fabric, in contrast to the former where rounds occur immediately (next
+clock cycle) one after the other.
+
+% superscalar also
 

### 2019-12-08 reports/paper.tex
wording

@@
 The core Simon cipher functionality is implemented as the core IP and is
-re-utilized to build three different accelerator types: memory-mapped
-(loosely-coupled), RoCC (tightly-coupled and hybrid). In essence the the
+re-utilized to build three different accelerator types: memory-mapped I/O
+(MMIO, loosely-coupled), RoCC (tightly-coupled and hybrid). In essence the the
 accelerators are built by constructing wrappers around the common core.
@@
 
-The memory-mapped accelerator can operate in two different ways: i) automatic
+The MMIO accelerator can operate in two different ways: i) automatic
 operation --- ECB mode only, in which all necessary rounds are performed over a word until
@@
 requests without intervention of the CPU, directly into the memory bus. The
-memory-mapped accelerator in the automatic mode comes in as second fastest. This
+MMIO accelerator in the automatic mode comes in as second fastest. This
 is also to be expected in comparison with the RoCC accelerator for example,
@@
 be used in-hardware to enable acceleration of ciphers, it is a proof-of-concept
-level rudimentary implementation.
+level, rudimentary implementation.
 

### 2019-12-08 reports/paper.tex
write more

@@
   systems in the security domain by implementing an IP core for cryptographic
-  primitive acceleration.
+  primitive acceleration. We also show a hybrid accelerator topology for
+  acceleration and/or secure memory storage which offers a speedup of 6x compared to a
+  pure software implementation.
   % results also go in here
@@
 To assemble an entire SoC for cycle-accurate simulation, UC Berkeley's Chipyard~\cite{Chipyard}
-is chosen.
+is chosen. Specifically, technologies used include:
+
+\subsubsection{RISC-V cores}
+
+There is already a variety of readily usable RISC-V cores out in the wild. To
+study different HWACC topologies, UC Berkeley's implementations are chosen; we
+select Rocket (in-order 5 stage pipeline, riscv64) and Berkeley out-of-order
+machine (BOOM).
+
+\subsubsection{RoCC interface}
+
+The RoCC interface is an interface developed for the Rocket RISC-V core that
+allows easy integration of HWACCs, effectively enabling the construction of
+tightly-coupled accelerators. This interface is also supported in UC Berkeley's
+BOOM implementation. In this paper, the terms tightly-coupled accelerator and
+RoCC accelerator are used interchangeably when talking about the specific
+implementations related to evaluation and results.
+
+The RISC-V ISA specifies 4 different opcodes, \texttt{custom0-3} which are used for passing data
+into and back the RoCC interface; with this mechanism, the HWACC is receives the
+contents of up to two CPU registers and optionally passes back a word to be stored in any of
+the CPU's registers as a result of the operation.
 
@@
 hierarchy. This allows the accelerator to directly request data to be loaded and
-stored, enabling two different modes of operation.
+stored, enabling two different modes of operation. Note that due to the
+architecture of the RoCC interface, the accelerator will have access to the
+coherent memory hierarchy at the L2 cache level.
 
@@
 
+Figure~\ref{fig:scatter} shows the relationship between number of instructions
+retired by processor and total number of cycles for the benchmark to finish in
+the in-order (rocket) core. Ultimately, the number of instructions retired is
+correlated to code size; it is clear that for the accelerator configurations
+that allow encryption in the CBC mode to be implemented, there is little
+overhead incurred by the extra operations (XORs), which are carried out by
+the CPU.
+
 \begin{figure}
@@
 
+The tools provided by the RISC-V community members enable computer architecture
+exploration in a very powerful way. This allowed for the exploration of
+different HWACC topologies; we found that there can be performance gains when
+using tightly-coupled accelerators and security gains.
+
+In order to achieve maximum performance/security, however, it is necessary to
+fully customize the microarchitecture and toolchain to fully orchestrate secure
+computations in the CPU's datapath, which will increase development costs.
+
 \bibliography{paper}

### 2019-12-09 reports/paper.tex
wording
synthesis results

@@
 
-\subsection{Full-scale SoC simulation}
+\subsection{Full SoC simulation}
 
@@
 dev kit is chosen for this task.
+
+We generate a system that targets Digilent's Arty FPGA board, then use Xilinx
+Vivado to perform synthesis and implementation and extract metrics.
 
@@
 \begin{itemize}
-\item Pure software: ECB and CBC mode
+\item Software only: ECB and CBC mode
 \item MMIO accelerator, single: ECB and CBC mode
@@
 adapter fabric, in contrast to the former where rounds occur immediately (next
-clock cycle) one after the other.
+clock cycle) one after the other. The MMIO accelerator in single mode greatly
+suffers from the need to access the memory bus for each operation, ultimately
+making it slower than software.
 
@@
 
+Synthesis and implementation are performed using Vivado. This is only done
+once, for the MMIO accelerator, as the core implementation of Simon is shared
+across all accelerators. Usage as reported by vivado is at 3119 LUTs and 2004
+flip flops, which account for approximately 17\% and 19.5\% of the total design
+(SoC) size.
+
+The somewhat large size of the accelerator design stems mainly from the
+unoptimized key expansion function, which accounts for roughly 75\% and 83.5\%
+of the flip flop and LUT usage for the entire accelerator. The round function
+accounts for the rest of the usage.
+
+\subsection{Power}
+
+Estimated power consumption is also reported after synthesis and implementation
+using Vivado. It is reported as 8mW for the simon accelerator alone --- the
+entire SoC power consumption is estimated at 252 mW (HWACC accounts for \approx 3\%).
+
+As is the case for area, power the key expansion is also responsible for the
+majority of power consumption, approximately 87.5\% of the total for the accelerator.
+
 \subsection{Security implications}
@@
     accelerators and toolchain must be modified to use customized instructions,
-    which can be configured for certain privilege levels only
+    which can be configured for certain privilege levels only.
 \end{itemize}

### 2019-12-09 reports/paper.tex
write more, almost done

@@
 
-\title{\textbf{Hardware accelerator topologies in heterogeneous systems: an evaluation in the
+\title{\textbf{Hardware accelerator coupling in heterogeneous systems: an evaluation in the
     security domain}}
-\author{Bruno Morais}
+\author{Bruno Morais \texttt{<soutomaiormunizmo.b@husky.neu.edu>}}
 \date{}
@@
   pure software implementation.
-  % results also go in here
 
@@
 
+The demand for power-efficient computing, specially on edge and/or embedded
+devices has continuously driven the development of hardware accelerators
+(HWACCs) to meet these power requirements. General-purpose computing units alone
+are too flexible and cannot achieve the same parallelism as a specialized
+accelerator. The growing complexity of algorithms, specially with the advent of
+widespread machine learning and security needs such as authentication, integrity
+verification and privacy, has pushed the boundaries of embedded systems,
+dramatically increasing the number of accelerators present in sophisticated
+embedded SoCs.
+
+With the number of HWACCs rapidly increasing, the use of typical memory mapped HWACC,
+which shares the memory bus of a general purpose CPU creates bottlenecks~\cite{TSS},
+specially for certain classes of applications, for instance streaming-based
+applications, where communication between HWACCs (function compositions) is a requirement.
+Figure~\ref{fig:loosely} shows the typical memory-mapped HWACC, also called a
+\textit{loosely-coupled} HWACC.
+
 \begin{figure}
@@
   \caption{Loosely-coupled HWACCs: typical memory mapped HWACC usage in a heterogenous architecture.}
+  \label{fig:loosely}
 \end{figure}
+
+In constrast with the \textit{loosely-coupled} accelerator which is external to
+the CPU datapath, an alternative topology is to bring the HWACC much closer, and
+effectively into the CPU datapath itself. Those are called
+\textit{tightly-coupled} HWACCs. Essentially, in this configuration, the HWACC
+can be seen as one of the CPU's functional units, dedicated to a certain
+specific task. Figure~\ref{fig:tightly} shows a simplified CPU datapath with
+tightly-coupled accelerators.
+
+While it is relatively straightforward to design accelerators and perform research using
+loosely-coupled accelerators by deploying them in FPGAs, for instance, research
+into tightly-coupled HWACCs has been historically prohibitive due to the need to
+have an easily modifiable processor implementation and all the necessary
+supporting tools such as compiler toolchain, simulators and a synthesis enabled
+design. The RISC-V project and its community have fostered the development of
+such a system, which is open source and user friendly, enabling much easier
+research of such a topology.
+
+Tightly-coupled accelerators are invaluable from a security perspective, not
+only to accelerate cryptographic functions but also to enable secure data
+storage. The main contribution of this work is the implementation of a HWACC
+that accelerates the Simon cipher and an analysis of the speedup provided by
+different couplings. We also show a hybrid tightly-coupled accelerator which has
+access to the on-chip coherent memory hierarchy and enables secure data storage
+and retrieval to/from main memory.
 
@@
     operating similarly to microarchitectural Functional Units (FUs).}
+  \label{fig:tightly}
 \end{figure}
@@
 
-\subsection{Hardware accelerators?}
-% Tightly vs loosely coupled hwaccs
+\subsection{Hardware accelerator coupling in heterogeneous systems}
+The usage of different couplings (tightly/loosely coupled) leads to mixed
+results depending on the domain of the application. Typical usage of HWACCs fall
+within the loosely-coupled category, which pays little attention to interaction
+with on-chip components such as caches~\cite{tightLoose}.
 
-\subsection{RISC-V instruction set extensions}
-% Xcrypto
+There is potential gain by moving accelerators into the CPU datapath and
+enabling leveraging the memory hierarchy to increase speedup. This incurs in
+more development costs, as discussed before when compared to loosely-coupled
+accelerators, which are more easily abstracted and do not need extensive
+modifications to the toolchain.
+
+\subsection{RISC-V cryptographic extensions}
+The RISC-V community has formed a group to specify ISA extensions for
+cryptographic primitives~\cite{RiscVCrypto}. The approach is similar to Intel's
+AES-NI~\cite{AESNI}, and is expected to support at least AES and SHA-2. These
+type of accelerators are tightly-coupled accelerators directly controlled by
+software instructions.
+
+There is also some independent work showcasing the implementation of accelerated
+cryptographic functions by means of instruction set extensions by the University
+of Bristol~\cite{xcrypto}. The XCrypto is part of a larger project and
+implements AES, SHA-2 and SHA-3.
 
@@
 flip flops, which account for approximately 17\% and 19.5\% of the total design
-(SoC) size.
+(SoC) size. The target FPGA has a total of 20800 and 41600 LUTs and flip flops
+available, respectively.
 
@@
 using Vivado. It is reported as 8mW for the simon accelerator alone --- the
-entire SoC power consumption is estimated at 252 mW (HWACC accounts for \approx 3\%).
+entire SoC power consumption is estimated at 252 mW (HWACC accounts for $\approx$ 3\%).
 

### 2019-12-10 reports/presentation.tex
partial presentation

\documentclass[dvipsnames]{beamer}
\usepackage{tikz}
\usepackage{standalone}
\usepackage{wrapfig}
\usetikzlibrary{positioning, calc, shapes, fit, backgrounds, patterns}
\addtobeamertemplate{navigation symbols}{}{%
  \usebeamerfont{footline}%
  \usebeamercolor[fg]{footline}%
  \hspace{1em}%
  \insertframenumber/\inserttotalframenumber
}
\setbeamercolor{footline}{fg=NavyBlue}
\setbeamerfont{footline}{series=\bfseries}
\title{Hardware accelerator coupling in heterogeneous systems: an evaluation in the
  security domain}
\author{Bruno S M M Morais}
\date{December 10, 2019}

\begin{document}

\maketitle

\begin{frame}{Heterogeneous systems}
  \begin{itemize}
  \item Specialized HWACCs required for energy efficient embedded / edge computing
  \item Explosion in \# of ACCs in recent SoCs, specially with deployment of
    machine learning, DSP algorithms for instance
  \end{itemize}
\end{frame}

\begin{frame}{Loosely-coupled accelerators}
  \begin{columns}[T]
    \begin{column}{0.35\textwidth}
      \resizebox{0.35\textwidth}{!}{
        \begin{minipage}{0.5\textwidth}
          \centering
          \include{media/loosely_acc}
        \end{minipage}
      }
    \end{column}
    \hfill
    \begin{column}{0.65\textwidth}
      \centering
      \begin{itemize}
      \item Access through shared memory bus
      \item Usually interrupts CPU when task is done
      \item With increase of \# of ACCs, communication becomes bottleneck
      \item CPU typically orchestrates compositions of HWACC functions
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Tightly-coupled accelerators}
  \begin{columns}[T]
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item ACC moved into CPU datapath
        \item Requires ISA modification/extensions
        \item More difficult to explore, requires extensive modification of
          $\mu$Architecture and tools
      \end{itemize}
    \end{column}
    \hfill
    \begin{column}{0.5\textwidth}
      %\centering
      \resizebox{0.45\textwidth}{!}{
        \begin{minipage}{0.75\textwidth}
          \centering
          \include{media/tightly_acc}
        \end{minipage}
      }
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{RISC-V ecosystem}
  \begin{columns}[T]
    \begin{column}{0.6\textwidth}
      \begin{itemize}
      \item FOSS ISA specification and many implementations
      \item ISA is built to be extensible
      \item RoCC interface enables attaching HWACCs to datapath easily
        \begin{itemize}
        \item 4 custom opcodes for routing to 4 HWACCs
        \item Contents of two registers passed into HWACC
        \item Optionally response from HWACC written to a register
        \item Optional interface for requests into L1 cache
        \end{itemize}
      \end{itemize}
    \end{column}
    \hfill
    \begin{column}{0.4\textwidth}
      \centering
      \includegraphics[width=0.75\textwidth]{media/Tall_2.pdf}
      \includegraphics[width=1.0\textwidth]{media/rocc.pdf}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{The Simon cipher family}
  \begin{columns}[T]
    \begin{column}{0.35\textwidth}
    \include{media/simonround}
    \end{column}
    \hfill
  \begin{column}{0.65\textwidth}
    \begin{itemize}
    \item Optimized for hardware implementations
    \item Only bitwise rotate, bitwise XOR and bitwise AND
    \item 64/128 (44 rounds) and 128/128 (128 rounds) configurations
    \end{itemize}
  \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Hybrid crypto accelerator}
  \begin{columns}[T]
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item Batch encrypt/decrypt
      \item Transparent encrypted memory load/store
      \item Direct access into coherent memory through DMA
      \item In this work, HWACC accesses into memory at L2 cache level
      \end{itemize}
    \end{column}
    \hfill
    \begin{column}{0.5\textwidth}
      % \centering
      \resizebox{0.3\textwidth}{!}{
        \begin{minipage}{0.5\textwidth}
          \centering
          \include{media/hybrid_acc}
        \end{minipage}
      }
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Experimental setup}
  \begin{minipage}[0.2\textheight]{\textwidth}
    \begin{columns}[T]
      \begin{column}{0.8\textwidth}
        \begin{itemize}
        \item Three Simon accelerators
        \begin{itemize}
        \item MMIO (loosely-coupled)
        \item RoCC (tightly-coupled)
        \item RoCC + DMA (hybrid)
          \end{itemize}
        \end{itemize}
      \end{column}
      \begin{column}{0.2\textwidth}
        \includegraphics[width=2.5cm]{media/cogs.jpeg}
      \end{column}
    \end{columns}
  \end{minipage}
  \begin{itemize}
  \item Both in-order (Rocket) and out-of-order (BOOM) cores
  \item Performance: eight benchmarks run on cycle-accurate simulations
    \begin{itemize}
    \item Software only: ECB and CBC mode
    \item MMIO accelerator, single: ECB and CBC mode
    \item MMIO accelerator, automatic: ECB mode
    \item Tightly-coupled accelerator: ECB and CBC mode
    \item Hybrid accelerator: ECB mode
    \end{itemize}
  \item Area \& power: HWACC synthesized for Xilinx FPGA, post-implementation
    metrics extracted
  \end{itemize}
\end{frame}

\begin{frame}{Results: performance}
  \begin{columns}[T]
  \begin{column}{0.5\textwidth}
  \includegraphics[width=1.0\textwidth]{media/ecb_speedup}
  \includegraphics[width=1.0\textwidth]{media/cbc_speedup}
  \end{column}
  \begin{column}{0.5\textwidth}
  \begin{itemize}
    \item Hybrid in batch mode is fastest, followed by regular MMIO
    \item Gains with RoCC accelerator, but is slower than 2-way BOOM SW only
    \item Need to understand RoCC interface timing better
    \item CBC mode performance very similar to EBC in comparable configurations
  \end{itemize}
  \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Results: area \& power}
\end{frame}

\begin{frame}{Results: security considerations}
\end{frame}

\begin{frame}{Future work}
\end{frame}

\begin{frame}{References}
\end{frame}

\begin{frame}{Questions?}
  \centering
  \huge\bfseries ?
\end{frame}

\end{document}

### 2019-12-10 reports/presentation.tex
write more

@@
   \item Both in-order (Rocket) and out-of-order (BOOM) cores
-  \item Performance: eight benchmarks run on cycle-accurate simulations
+  \item SoC built with UC Berkeley's Chipyard (HWACCs attached)
+  \item Performance: eight benchmarks run on SoC cycle-accurate simulations
     \begin{itemize}
@@
 \begin{frame}{Results: area \& power}
+  \begin{itemize}
+  \item Arty FPGA with 20800 LUTs / 41600 FFs available
+  \item Usage reports 3119 LUTs and 2004 FFs, $\approx$ 17\% and 19.5\% of the
+    total design (SoC) size
+  \item Somewhat large usage due to unoptimized key expansion function
+  \item ACC power consumption estimated at 8mW, $\approx$ 3\% of total SoC
+    estimated power consumption (252mW)
+  \item Key expansion function also accounts for most of power consumption at
+    $\approx$ 87.5\% of ACC consumption
+  \end{itemize}
 \end{frame}
@@
 \begin{frame}{Future work}
+  \begin{itemize}
+  \item More flexible accelerators, multiple encryption modes, parallelized decryption
+  \item Fully custom HWACC interface \& instructions, not RoCC
+  \item Privileged HWACC access, OS support (multi-context)
+  \end{itemize}
 \end{frame}
